---
title: "Project 1 DATA 607"
author: "Neil Hodgkinson"
date: "2022-09-25"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library (readr)
library(stringr)
library(tidyverse)
library(dbplyr)
library(data.table)

#urlfile="https://raw.githubusercontent.com/Nhodgkinson/DATA_607_project1/main/tournamentinfo.txt"




tournamentinfo <- paste(readLines("https://raw.githubusercontent.com/Nhodgkinson/DATA_607_project1/main/tournamentinfo.txt"), collapse = '\n')

df<-str_remove_all(tournamentinfo, "(-)\\1{2,}")

mydata<-read_delim(df, delim="|")

mydata<-mydata[-1,]








```

## R Markdown
String extracting data to create new columns

```{r }

#player num column returns only digit values
player_num1 <- str_extract(mydata$` Pair `, "\\d+")
mydata$player_num1<-player_num1

#player state column returns non digit values 
player_state <- str_extract(mydata$` Pair `, "\\D+")
mydata$player_state<-player_state


#player pre rating column
player_pre_rating <- str_extract(mydata$` Player Name                     `, "(\\bR: *)\\d{3,}")
#this next line removes the : from the new player_pre_rating value so I only have digits
player_pre_rating <- str_extract(player_pre_rating, "\\d{3,}")
mydata$player_pre_rating<-player_pre_rating

#player name column
player_name <- str_extract(mydata$` Player Name                     `, "\\D*")
mydata$player_name <-player_name

#player total column
player_total <- str_extract(mydata$Total, "\\d(\\b.)\\d")
mydata$player_total <- player_total


mydata<-subset(mydata, select=-c(1:3))



```


#Subset data
```{r}
df<-mydata[!is.na(mydata$player_pre_rating),]
mydata<-subset(mydata, select=-c(8,10,11))

mydata<-mydata[!is.na(mydata$player_num1),]

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
df_new <- cbind(df, mydata)
df_new<-subset(df_new, select=-c(1:9,12,13))
df_new[,c(10:12,1:9)]

opp_data <- df_new[,c(10,3:9)] 
  
  
  
  


```
#naming rows

I renamed the rows and pulled the numeric values out.
```{r}
player_num <- opp_data$player_num1
opp_data$player_num<-player_num

rnd1 <- str_extract(opp_data$Round...4, "(\\b *)\\d{1,}")
opp_data$rnd1 <-rnd1

rnd2 <- str_extract(opp_data$Round...5, "(\\b *)\\d{1,}")
opp_data$rnd2 <-rnd2

rnd3 <- str_extract(opp_data$Round...6, "(\\b *)\\d{1,}")
opp_data$rnd3 <-rnd3

rnd4 <- str_extract(opp_data$Round...7, "(\\b *)\\d{1,}")
opp_data$rnd4 <-rnd4

rnd5 <- str_extract(opp_data$Round...8, "(\\b *)\\d{1,}")
opp_data$rnd5 <-rnd5

rnd6 <- str_extract(opp_data$Round...9, "(\\b *)\\d{1,}")
opp_data$rnd6 <-rnd6

rnd7 <- str_extract(opp_data$Round...10, "(\\b *)\\d{1,}")
opp_data$rnd7 <-rnd7

opp_data<-subset(opp_data, select=-c(2:9))

df_new$player_pre_rating<- as.integer(df_new$player_pre_rating)

```
#multiple attempts and not succeeding
I looked up a few possible solutions and I'm not able to figure it out. I first start out by removing the N/A and replacing with blanks. Then I got stuck and could not figure this out.
```{r}
opp_data[is.na(opp_data)] <- ""

opp_data <- opp_data %>%
  left_join(df_new, c("player_num1" = "player_num1")) %>% select (player_num1, player_pre_rating) %>%
  group_by (player_num1) %>%
  summarize(avg_opp_rating=  round(mean(player_pre_rating),0))

```
#Final
Ran out of time and could not figure out how to avg the scores. I wanted to create a second table called opp_data and ref the play num on df_new to get an avg score.
```{r}
chess_final <- df_new %>%
  left_join(opp_data, c("player_num1" = "player_num1")) %>% select (player_name, player_state, player_total, player_pre_rating,avg_opp_rating)
```
#csv 

```{r}
write.csv(chess_final,"tournmnt_data.csv",row.names = FALSE)
```

